\bf Hierarchical Network Structure Promotes Dynamical Robustness

### 2015-07-14 tex/overview.tex
remind reader of reuse of n

The decomposition of a digraph into SCCs corresponds to a block triangular decomposition of its adjacency matrix.  Say that the graph $G$ has SCCs $C_1, C_2, \ldots C_n$, which have been labelled in such a way that there are no links from vertices in component $C_i$ to component $C_j$ when $i < j$.  Label the vertices in such a way that $V_1, \ldots, V_{n_1}$ belong to $C_1$, $V_{n_1 + 1}, \ldots, V_{n_2}$ belong to $C_2$, etc.  Then, if we choose basis vectors corresponding to this labelling of the vertices, we will have $a_{ij} = 0$ whenever $i$ and $j$ correspond to different components and $i > j$.  This condition is equivalent to stating that the matrix is block triangular with blocks of size $n_1, n_2, \ldots$.

>>>>

The decomposition of a digraph into SCCs corresponds to a block triangular decomposition of its adjacency matrix.  Say that the graph $G$ has SCCs $C_1, C_2, \ldots C_n$, where we now use $n$ with no index to specify the number of SCCs, which have been labelled in such a way that there are no links from vertices in component $C_i$ to component $C_j$ when $i < j$.  Label the vertices in such a way that $V_1, \ldots, V_{n_1}$ belong to $C_1$, $V_{n_1 + 1}, \ldots, V_{n_2}$ belong to $C_2$, etc.  Then, if we choose basis vectors corresponding to this labelling of the vertices, we will have $a_{ij} = 0$ whenever $i$ and $j$ correspond to different components and $i > j$.  This condition is equivalent to stating that the matrix is block triangular with blocks of size $n_1, n_2, \ldots$.
